Extensibility and Composability of a Multi-Stencil Domain Specific Framework

### 2017-03-07 ARTICLES/IJPP/articleR1/evaluation.tex
corrections figures

\begin{figure}[th]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/analytic/times.pdf}
  \caption{Computation vs communication times for a single time iteration using the data parallelization technique.}
  \label{fig:limit}
  %\CP{es tu sûr que le temps soit en puissance de 2 et pas en puissance de 10? C'est strange.}
\end{center}\end{figure}

@@

\begin{figure}[!h]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/analytic/tth.pdf}
  \caption{Execution times (seconds) for a single time iteration of $T_{COM1}$ and $T_{COM2} + T_{task}$ for 8 cores for task parallelization. Verification of the Equation~(\ref{eq:hyb}).}
  \label{fig:tth2}
%\CP{Time en puissance de 2 ou de 10 ?}
\end{center}\end{figure}

@@

In this section we propose an evaluation of the fusion optimization. From the $TSP$ tree computed by MSC it may be possible, according to some specific conditions, to merge the domain loops of some kernels, thus optimizing the use of cache memories. This optimization is called a fusion and has been introduced in Section\ref{sect:fusion}. Three fusion optimizations
%\CP{les rappeler !}
%
have been formally detailed in Section~\ref{sect:fusion}. The two first ones of Figures~\ref{fig:fus1} and~\ref{fig:fus2}~\vpageref{fig:fus2} have been automatically detected by MSF in our case study (\ie scatter optimization has not been detected).
\CP{Et la troisieme ?}

@@

\begin{figure}[!h]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout2_close_median.pdf}
  \caption{Strong scaling on a 500x500 domain size with $200$ time iterations. Blue curves represent strong scaling for data parallelism with and without fusion. Red curves represent strong scaling by using 2 cores per MPI process dedicated to tasks, with and without fusion.}
  \label{fig:fusion1}
  \CP{ERREUR DANS LEGENDES !!}
\end{center}\end{figure}

@@

\begin{figure}[!h]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout8_close_median.pdf}
  \caption{Strong scaling on a 500x500 domain size with $200$ time iterations. Blue curves represent strong scaling for data parallelism with and without fusion, thus are exactly the same than blue curves of Fig.~\ref{fig:fusion1}. Red curves represent strong scaling by using 8 cores per MPI process dedicated to tasks, with and without fusion.}
  \label{fig:fusion2}
    \CP{ERREUR DANS LEGENDES.}
\end{center}\end{figure}
In conclusion, if fusion optimization incurs a too large reduction of the number of tasks to feed dedicated cores, the problem observed for 16 cores in Figure~\ref{fig:close} happens earlier which reduces performance. For this reason, MSF performs fusions only when data parallelization is used alone. This choice could be more intelligent but this is the subject of future work.

>>>>

\begin{figure}[th]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/analytic/times2.pdf}
  \caption{Computation vs communication times for a single time iteration using the data parallelization technique.}
  \label{fig:limit}
  %\CP{es tu sûr que le temps soit en puissance de 2 et pas en puissance de 10? C'est strange.}
\end{center}\end{figure}

@@

\begin{figure}[!h]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/analytic/tth2.pdf}
  \caption{Execution times (seconds) for a single time iteration of $T_{COM1}$ and $T_{COM2} + T_{task}$ for 8 cores for task parallelization. Verification of the Equation~(\ref{eq:hyb}).}
  \label{fig:tth2}
%\CP{Time en puissance de 2 ou de 10 ?}
\end{center}\end{figure}

@@

In this section we propose an evaluation of the fusion optimization. From the $TSP$ tree computed by MSC it may be possible, according to some specific conditions, to merge the domain loops of some kernels, thus optimizing the use of cache memories. This kind of optimization is called a fusion and has been introduced in Section\ref{sect:fusion}. Three fusion optimizations
%\CP{les rappeler !}
%
have been formally detailed in Section~\ref{sect:fusion}. The two first ones of Figures~\ref{fig:fus1} and~\ref{fig:fus2}~\vpageref{fig:fus2} have been automatically detected by MSF in our case study (\ie the third scatter optimization of Fig.~\ref{fig:fus3} has not been detected).
%\CP{Et la troisieme ?}

@@

\begin{figure}[!h]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout2_close_median.pdf}
  \caption{Strong scaling on a 500x500 domain size with $200$ time iterations. Blue curves represent strong scaling for data parallelism with and without fusion. Red curves represent strong scaling by using 2 cores per MPI process dedicated to tasks, with and without fusion.}
  \label{fig:fusion1}
  %\CP{ERREUR DANS LEGENDES !!}
\end{center}\end{figure}

@@

\begin{figure}[!h]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout8_close_median.pdf}
  \caption{Strong scaling on a 500x500 domain size with $200$ time iterations. Blue curves represent strong scaling for data parallelism with and without fusion, thus are exactly the same than blue curves of Fig.~\ref{fig:fusion1}. Red curves represent strong scaling by using 8 cores per MPI process dedicated to tasks, with and without fusion.}
  \label{fig:fusion2}
    %\CP{ERREUR DANS LEGENDES.}
\end{center}\end{figure}
In conclusion, if fusion optimization incurs a too large reduction of the number of tasks to feed dedicated cores, the problem observed for 16 cores in Figure~\ref{fig:close} happens earlier which reduces performance. For this reason, MSF performs fusions only when data parallelization is used alone. This choice could be more intelligent but this is the subject of future work.
